---
# This file generates AGENTS.md in the package root.
# It is not part of the package build or the pkgdown site.
# To regenerate it, run from the package root:
#   rmarkdown::render("vignettes/_AGENTS.Rmd", output_file = file.path("AGENTS.md"), output_dir = ".")
output:
  github_document:
    html_preview: false
params:
  url: "https://raw.githubusercontent.com/insightsengineering/teal/refs/heads/main/SHARED_AGENTS.md"
---
# teal.logger R Package Development Guide

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Overview

`teal.logger` is part of the `teal` framework and provides functions to log changes on teal apps.

It provides 4 functions:

- `register_handlers()` and `register_logger()`: Register handlers and loggers as `logger`.
- `log_shiny_input_changes()` and `log_system_info()`: Logs input values and the system information.
- `suppress_logs()` Suppress logs mainly for tests.

For details about teal.logger configuration check `vignettes/teal-logger.Rmd`

## Development Context

The main feature of this package is to provide `teal` apps with functionality to log the state.

### Relationships with other packages

Direct dependencies:

- `logger`: Extends the logger package with some custom settings.

Usage in other framework packages:

- It is used on `teal`, `teal.modules.clinical`, `teal.modules.general`, `teal.picks`, `teal.slice`, `teal.transform` and other module packages


```{r teal_content, echo=FALSE, results='asis'}
# Append common shared instructions from teal framework
common_agents_url <- params$url
common_agents_path <- tempfile()
download.file(url = common_agents_url, destfile = common_agents_path, quiet = TRUE)
common_agents_shared <- readLines(common_agents_path)
# remove section intended only for module packages
remove_sections <- c("<!-- (Begins|Ends) Module Section")
Reduce(
  function(x, y) {
    delim <- grep(y, x)
    if (length(delim) == 0) {
      return(x)
    } else if (length(delim) != 2) {
      stop("Section delimiters are not balanced")
    }
    x[-1 * seq(from = delim[1], to = delim[2])]
  },
  remove_sections,
  init = common_agents_shared
) |>
  cat(sep = "\n")
```
